# Data {#sec-data}
## Integrating your R data workflow into this thesis template
- You will have R/Python data analysis scripts which do various things to raw data from your thesis.
- You may want to contain this all within the thesis repository to keep everything neat
- You could do something like I have done below in @sec-R
- Or you could do your analysis directly in the chapter .qmd files. But probably that would make your .qmd files quite long and unpleasant!

### R code {#sec-R}
Remember when you source things from within your chapters/.qmd files the current working directory is in the chapters directory. Therefore define the filepath relative to there. Refer to the table and figure in text with @tbl-summary-table and @fig-airquality.

```{r}
#| echo: true
#| warning: false
#| message: false
source("scripts/chap1.R")
```

```{r}
#| label: fig-airquality
#| echo: true
#| warning: false
#| message: false
#| fig-cap: "Air Quality"

plot_temp_ozone
```

```{r}
#| label: tbl-summary-table
#| echo: true
#| warning: false
#| message: false
#| tbl-cap: "Summary Table"

summary_table
```

I have put this table in an appendix to show how that would work. Please see Appendix A @tbl-appendix-summary-table. 

## Example of Quarto Callout Blocks

Quarto allows us to add various types of callouts to emphasize key information in our documents.

### Callout Examples

::: {.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

::: {.callout-tip}
## Tip with Title

This is an example of a callout with a title.
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

::: {.callout-tip title="Tip with Title"}
This is a callout with a title.
:::


::: {.callout-note appearance="simple"}

## Pay Attention

Using callouts is an effective way to highlight content that your reader give special consideration or attention.

:::
